---
title: "Gun Control chi squared"
author: "Madeline Gorchels and Renee Albrecht"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

What did the fish say when it swam into a wall? 

Dam!! 

Where did the general put his armies?

Into his sleevies! 

I am reaaaally stumped on this one!! 

Why are there spaces between your fingers? 


1. Loading the tidyverse and reading in the data 
```{r}
library(tidyverse)
gc_df = read_csv("gc_df.csv")
#View(gc_df)

get_guns = gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender) 
  
  rownames(get_guns) =c("Female", "Male")
#View(get_guns)
```

I am the collaborator, Renee Albrecht, and I am going to do chi-square.  

Chi-sqaure question: 

Is there a significant difference in gun control perspectives (as related to access to guns) for males and females?
Is there a significant association between sex and gun control recommendations? 
Is perception of gun control access independent of sex? 

All of the above questions are asking the same thing. 

```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)

guns_prop

# Perform chi-square

guns_x2 <- chisq.test(get_guns)
guns_x2


```

Recommended government action on gun access differes significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ..., p < 0.001)

